Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-06-20 final/cleanpaper/pedestrian_forecasting_iros_2017.tex
Try to fix type 3
making small changes to the text to make it ready for final version

\documentclass[letterpaper,10pt,conference]{ieeetran}
%\usepackage{times}

\IEEEoverridecommandlockouts 
%\overrideIEEEmargins   % Needed to meet printer requirements.
\usepackage[T1]{fontenc}

@@

%%% first author
\author{Henry O. Jacobs, Owen K. Hughes, Matthew Johnson-Roberson, and Ram Vasudevan
 \thanks{ H.O. Jacobs, O.K. Hughes, M. Johnson-Roberson, and R.~Vasudevan are with the University of Michigan, Ann Arbor, MI 48109
{\scriptsize \{\texttt{hojacobs,owhughes,mattjr,ramv}\}~\texttt{@umich.edu}}}
\thanks{This material is based upon work supported by Ford Motor Company and the National Science Foundation under Grant No. 1562612.}
}

@@

\begin{abstract}
The success of autonomous systems will depend upon their ability to safely navigate human-centric environments.
This motivates the need for a real-time, probabilistic forecasting algorithm for pedestrians, cyclists, and other agents since these predictions will form a necessary step in assessing the risk of any action.
This paper presents a novel approach to probabilistic forecasting for pedestrians based on weighted sums of ordinary differential equations that are learned from historical trajectory information within a fixed scene.
The resulting algorithm is embarrassingly parallel and is able to work at real-time speeds using a naive Python implementation.
The quality of predicted locations of agents generated by the proposed algorithm is validated on a variety of examples and considerably higher than existing state of the art approaches over long time horizons.
%When compared with MDP-based methods, this algorithm 
\end{abstract}

@@

Autonomous systems are increasingly being deployed in and around humans. 
The ability to accurately model and anticipate human behavior is critical to maximizing safety, confidence, and effectiveness of these systems in human-centric environments. 
The stochasticity of humans necessitates a probabilistic approach to capture the likelihood of an action over a set of possible behaviors. 
Since the set of plausible human behaviors is vast, this work focuses on anticipating the possible future locations of pedestrians within a bounded area. 
This problem is critical in many application domains such as enabling personal robots to navigate in crowded environments, managing pedestrian flow in smart cities, and synthesizing safe controllers for autonomous vehicles (AV).

@@

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses. The dot is the starting point of the trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. The presented algorithm took $0.00465$s per frame in a Python implementation. }
	\label{fig:gates-1-2}
	\vspace*{-0.7cm}
\end{figure}

@@

\begin{algorithm}[t]
		  \caption{Algorithm to compute  $\rho_t$ for each $t \in  \{\Delta t, 2 \Delta t, \dots, N_t \Delta t$\}.}
		  \label{alg:1}
		  \begin{algorithmic}[1]
		    \Require $\bar{s} > 0$, $N_t \in \mathbb{N}$, $\Delta t > 0$,  $ \{ X_k \}_{k=1}^{n}$, $\hat{x}_0$, $\hat{v}_0$, $\Gamma_L( \hat{x}_0, N_x)$, $\Pr(x_0 \mid M), \Pr(x_0 \mid \hat{x}_0), \Pr(v_0 \mid \hat{v}_0 ), \Pr(M \in \mathcal{M}), \text{ and } \Pr(s \mid k)$.
		    \For {$\ell \in \{1,\dots,N_t\}$}
		    \State Compute $\Phi_{k,1}^{ \pm \bar{s} \ell \Delta t}( x_0^{i,j} )$ for all $x_0^{i,j} \in \Gamma_L( \hat{x}_0 ; N_x)$ and \hspace*{12pt} for all $k \in  \{1,\dots, n\}$.
		    \For {$m \in \{-\ell,\dots,\ell\}$}
		    \State Compute $W(k,s,i,j,\hat{x}_0)$ for $s = \bar{s} m / \ell$ for all \hspace*{28pt} $i,j\in \{-N_x,\dots, N_x\}$ and $k\in \{1,\dots,n\}$.
		    \EndFor  
		    \State Compute $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
%		    \State Construct a $\mathcal{O}( \Delta x + \bar{s}/\ell + \varepsilon_{\rm tol})$ approximation of $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
		    \hspace*{12pt} with partition $\mathcal{P}_\ell$ of \eqref{eq:partition}.\label{alg1:step2}
		    \State Apply Bayes' Theorem to obtain $\Pr(\check{x}_t \mid \hat{x}_0, \hat{v}_0)$.
		    \State Compute $\rho_t(x_t)$ at $t= \ell \cdot \Delta t$ via \eqref{eq:convolve}.
		    \EndFor
		  \end{algorithmic}
\end{algorithm}

@@

	\vspace{0.2cm}
	\hspace{.5cm}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 2.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 8.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 12.33s$
	\end{minipage}	
	\caption{Scene 2}
%	\caption{\rtext{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle. The algorithm in \cite{Alahi2016} is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}}
%	\reversemarginpar\marginnote{\#4.8}
	\label{fig:death-1-2}
	\end{subfigure}
	\caption{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle. The algorithm in \cite{Alahi2016} is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}
	\vspace{-0.7cm}
\end{figure*}

@@

\begin{table}
	\begin{center}
		\caption{Comparison of runtimes of the various algorithms.}
		\label{tab:time}
		\renewcommand{\arraystretch}{1.5}% Spread rows out...
		\begin{tabular}{||c | c c  c c ||} 
			\hline
			& Our Algorithm & Random Walk & Kitani et al. & S-LSTM \\ [0.5ex] 
			\hline 
			$\frac{\mathrm{time}}{\mathrm{frame}}$ & 0.00443s & 2.1E-7s & 0.0706s & 0.0134s \\
			\hline
		\end{tabular}
	\end{center}
	\vspace*{-0.6cm}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/the_results.eps}
	\caption{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the S-LSTM \cite{Alahi2016} model $100$ times to extract a less concentrated probability distribution from their algorithm.}
	\label{fig:auc_vs_time}
	\vspace*{-0.75cm}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is known.}
	\label{fig:mhd_vs_time}
	\vspace*{-0.7cm}
\end{figure}

>>>>

\documentclass[letterpaper,10pt,journal,twoside]{ieeetran}
%\usepackage{times}

%\IEEEoverridecommandlockouts 
%\overrideIEEEmargins   % Needed to meet printer requirements.
%\usepackage[T1]{fontenc}

\markboth{IEEE Robotics and Automation Letters. Preprint Version. Accepted June, 2017}
{Jacobs \MakeLowercase{\textit{et al.}}: Real-Time Certified Probabilistic Pedestrian Forecasting}

@@

%%% first author
\author{Henry O. Jacobs$^{1}$, Owen K. Hughes$^{1}$, Matthew Johnson-Roberson$^{1}$, and Ram Vasudevan$^{1}$
\thanks{Manuscript received: February 15, 2017; Revised May 8, 2017; Accepted June 5, 2017.}
\thanks{This paper was recommended for publication by Wan Kyun Chung upon evaluation of the Associate Editor and Reviewers comments. 
This material is based upon work supported by Ford Motor Company and the National Science Foundation under Grant No. 1562612.}
 \thanks{$^{1}$H.O. Jacobs, O.K. Hughes, M. Johnson-Roberson, and R.~Vasudevan are with the University of Michigan, Ann Arbor, MI 48109
{\scriptsize \{\texttt{hojacobs,owhughes,mattjr,ramv}\}~\texttt{@umich.edu}}}
}

@@

\begin{abstract}
The success of autonomous systems will depend upon their ability to safely navigate human-centric environments.
This motivates the need for a real-time, probabilistic forecasting algorithm for pedestrians, cyclists, and other agents since these predictions will form a necessary step in assessing the risk of any action.
This paper presents a novel approach to probabilistic forecasting for pedestrians based on weighted sums of ordinary differential equations that are learned from historical trajectory information within a fixed scene.
The resulting algorithm is embarrassingly parallel and is able to work at real-time speeds using a naive Python implementation.
The quality of predicted locations of agents generated by the proposed algorithm is validated on a variety of examples and considerably higher than existing state of the art approaches over long time horizons.
%When compared with MDP-based methods, this algorithm 
\end{abstract}
\begin{IEEEkeywords}
Optimization and Optimal Control and Human Detection \& Tracking
\end{IEEEkeywords}

@@

\IEEEPARstart{A}{utonomous} systems are increasingly being deployed in and around humans. 
The ability to accurately model and anticipate human behavior is critical to maximizing safety, confidence, and effectiveness of these systems in human-centric environments. 
The stochasticity of humans necessitates a probabilistic approach to capture the likelihood of an action over a set of possible behaviors. 
Since the set of plausible human behaviors is vast, this work focuses on anticipating the possible future locations of pedestrians within a bounded area. 
This problem is critical in many application domains such as enabling personal robots to navigate in crowded environments, managing pedestrian flow in smart cities, and synthesizing safe controllers for autonomous vehicles (AV).

@@

	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=235.jpg}
		\caption{$t=7.83s$}
	\end{subfigure}
	\begin{subfigure}[b]{.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/FirstPage/gates_1_2_t=345.jpg}
		\caption{$t=11.5s$}
	\end{subfigure}
	\caption{The performance of the presented algorithm captures the most probable routes that a pedestrian chooses. The dot is the starting point of the trajectory, the diamond is the position at time $t$, and the X is the end of the trajectory. The likelihood of detection is depicted using the \textit{virdis} color palette. The presented algorithm took $0.00465$s per frame in a Python implementation. }
	\label{fig:gates-1-2}
%	\vspace*{-0.7cm}
\end{figure}

@@

\begin{algorithm}[b]

		  \caption{Algorithm to compute  $\rho_t$ for each $t \in  \{\Delta t, 2 \Delta t, \dots, N_t \Delta t$\}.}
		  \label{alg:1}
		  \begin{algorithmic}[1]
		    \Require $\bar{s} > 0$, $N_t \in \mathbb{N}$, $\Delta t > 0$,  $ \{ X_k \}_{k=1}^{n}$, $\hat{x}_0$, $\hat{v}_0$, $\Gamma_L( \hat{x}_0, N_x)$, $\Pr(x_0 \mid M), \Pr(x_0 \mid \hat{x}_0), \Pr(v_0 \mid \hat{v}_0 ), \Pr(M \in \mathcal{M}), \text{ and } \Pr(s \mid k)$.
		    \For {$\ell \in \{1,\dots,N_t\}$}
		    \State Compute $\Phi_{k,1}^{ \pm \bar{s} \ell \Delta t}( x_0^{i,j} )$ for all $x_0^{i,j} \in \Gamma_L( \hat{x}_0 ; N_x)$ and \hspace*{12pt} for all $k \in  \{1,\dots, n\}$.
		    \For {$m \in \{-\ell,\dots,\ell\}$}
		    \State Compute $W(k,s,i,j,\hat{x}_0)$ for $s = \bar{s} m / \ell$ for all \hspace*{28pt} $i,j\in \{-N_x,\dots, N_x\}$ and $k\in \{1,\dots,n\}$.
		    \EndFor  
		    \State Compute $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
%		    \State Construct a $\mathcal{O}( \Delta x + \bar{s}/\ell + \varepsilon_{\rm tol})$ approximation of $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
		    \hspace*{12pt} with partition $\mathcal{P}_\ell$ of \eqref{eq:partition}.\label{alg1:step2}
		    \State Apply Bayes' Theorem to obtain $\Pr(\check{x}_t \mid \hat{x}_0, \hat{v}_0)$.
		    \State Compute $\rho_t(x_t)$ at $t= \ell \cdot \Delta t$ via \eqref{eq:convolve}.
		    \EndFor
		  \end{algorithmic}  
\end{algorithm}

@@

	\vspace{0.2cm}
	\hspace{.5cm}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 2.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 8.33s$
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
		\centering
		$t = 12.33s$
	\end{minipage}	
	\caption{Scene 2}
%	\caption{\rtext{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle. The algorithm in \cite{Alahi2016} is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}}
%	\reversemarginpar\marginnote{\#4.8}
	\label{fig:death-1-2}
	\end{subfigure}
	\caption{An illustration of the predictions generated by the various algorithms. In this figure, the dot is the start point of the test trajectory, the diamond is the position at time t, and the X is the end of the trajectory. The likelihood of detection is depicted using the virdis color palette. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle. The algorithm in \cite{Alahi2016} is confident and close to the trajectory at small times, but their lack of a motion model causes their prediction to compress into a point at intermediate time scales.}
%	\vspace{-0.7cm}
\end{figure*}

@@

\begin{table}
	\begin{center}
		\caption{Comparison of runtimes of the various algorithms.}
		\label{tab:time}
		\renewcommand{\arraystretch}{1.5}% Spread rows out...
		\begin{tabular}{||c | c c  c c ||} 
			\hline
			& Our Algorithm & Random Walk & Kitani et al. & S-LSTM \\ [0.5ex] 
			\hline 
			$\frac{\mathrm{time}}{\mathrm{frame}}$ & 0.00443s & 2.1E-7s & 0.0706s & 0.0134s \\
			\hline
		\end{tabular}
	\end{center}
%	\vspace*{-0.6cm}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/the_results.eps}
	\caption{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate. We sampled the S-LSTM \cite{Alahi2016} model $100$ times to extract a less concentrated probability distribution from their algorithm.}
	\label{fig:auc_vs_time}
%	\vspace*{-0.75cm}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{./figures/MHD_results.eps}
	\caption{A comparison of the MHD from the ground truth of the pedestrian to a 1000 point samples from each distribution. The method from \cite{Alahi2016} does well at short time scales since it places a highly confident distribution at the given initial position of the pedestrian, but the method developed in this paper outperforms all others at intermediate times. \cite{Kitani2012}, which requires the end point of each trajectory, outperforms all other algorithms at longer time scales since they assume that the end point of the trajectory is known.}
	\label{fig:mhd_vs_time}
%	\vspace*{-0.7cm}
\end{figure}
